The Effect of Episodic Retrieval on Inhibition in Task Switching

### 2016-09-16 Episodic Retrieval & Inhibition/Manuscript Files/main.tex
folder re-structure
new version of episodic retrieval paper

\note{{\bf Word Count:} 3,280 (Main body, not including abstract or references.)}
% \note{{\bf Under Review---Please, no direct quotes.}}

@@

\authornote{Please address correspondence to James A. Grange, School of Psychology, Dorothy Hodgkin Building, Keele University, Keele, UK, ST5 5BG. Email: grange.jim@gmail.com. All raw data and analysis code are available to download at http://bit.ly/1OgH9v0.}

@@

\abstract{Inhibition in task switching is inferred from n--2 repetition costs: the observation that AB$A$ task switching sequences are responded to slower than CB$A$ sequences. This is thought to reflect the persisting inhibition of task A, which slows re-activation attempts. \cite{Mayr2002} reported an experiment testing a critical non-inhibitory account of this effect, namely episodic retrieval: If the trial parameters for task A match across an ABA sequence, responses should be facilitated due to priming from episodic retrieval; a cost would occur if trial parameters mismatch. In a rule-switching paradigm, Mayr reported no significant difference in n--2 repetition cost when the trial parameters repeated or switched across an ABA sequence, in contrast to the episodic retrieval account. This conclusion rests on accepting a null hypothesis, which cannot be achieved with null hypothesis significance testing. Here we provide a replication of the critical aspects of Mayr's design. Using Bayesian analysis to quantify evidence for or against a null hypothesis, we find evidence for reduced n--2 repetition costs when trial parameters repeat compared to when they switch. In contrast to Mayr's conclusion, we suggest that episodic retrieval can influence the measure of inhibition in task switching, although it cannot explain it entirely.}

\keywords{Task switching; inhibition, episodic retrieval, cognitive control}

@@

How the cognitive system solves the stability--flexibility dilemma has been studied using the task switching paradigm \citep{Grange2014a,Kiesel2010,Vandierendonck2010}, wherein participants have to make speeded responses to simple cognitive tasks. For example, participants might be presented with number stimuli, and be asked to switch between judging whether the stimulus is odd/even or lower/higher than five. One cognitive process thought to be essential for task switching performance is the inhibition of competing tasks. Evidence for inhibition comes from the backward inhibition paradigm \citep{Koch2010, Mayr2000}, where participants are required to switch between three tasks (A, B, and C).  It is a consistent finding that AB$A$ task switching sequences are performed slower and with less accuracy than CB$A$ sequences. This \emph{n--2 task repetition cost} is thought to reflect the persisting inhibition of task A in an ABA sequence, which hinders its re-activation in the last trial of the triplet.

The n--2 task repetition cost is important as it appears to be robust against non-inhibitory explanations \citep{Mayr2007}. One potential explanation of the n--2 task repetition cost that does not assume inhibition was explored by \cite{Mayr2002}. This \emph{episodic retrieval} account \citep{Neill1997} suggests (adapted to a task switching context) that when a task has been performed an episodic trace of trial parameters (such as the cue, stimulus characteristics, and the response made) is stored in memory. When this task is cued again, retrieval of the most recent episodic trace occurs. If the parameters of the presented trial differ from that of the retrieved episode (e.g., a different response is required), a mismatch cost occurs relative to if the retrieved episode matches parameters of the current trial (which will prime performance). Thus, according to this account, n--2 task repetition costs reflect a mismatch cost, as trial parameters typically differ between both instances of task A in an ABA sequence.

\cite{Mayr2002} assessed this alternative explanation by developing a paradigm where the match between trial parameters across an ABA sequence could be manipulated (see Figure \ref{fig:mayrExperiment}). Participants were required to apply a spatial transformation of a target's location according to one of three stimulus--response rules (vertical, horizontal, or diagonal transformations). For example, if the target is in the bottom-left of the display and the current rule is ``vertical'', the correct response would be an upper-left response (as this reflects a vertical transformation of a bottom-left target). The parameters that might be stored in an episodic trace include (at least) the cue presented, the target's location, and the response made. In this paradigm, trial parameters can either match or mismatch across ABA and CBA sequences\footnote{Note that with one cue per task, the cue for task A will always be the same across an ABA sequence.}. For example, if the target is in the same location for task A across an ABA sequence, the same response will be required (i.e., an n--2 response repetition). In this case, the episodic retrieval account would predict facilitated performance relative to an n--2 response switch as in the former case the current trial parameters match perfectly the retrieved episodic trace. Thus, the episodic account would predict reduced n--2 task repetition costs for n--2 response repetitions compared to n--2 response switches (where there is a mismatch between trial parameters and the retrieved episodic trace).

\begin{figure}
\begin{center}
\includegraphics[width = \textwidth]{Images/mayrExperiment.pdf}
\caption{Schematic overview of Mayr's (2002) experimental procedure. The arrows are not displayed to participants, but reflect the spatial transformation required according to the given rule. See text for details.}
\label{fig:mayrExperiment}
\end{center}
\end{figure}

\cite{Mayr2002} found no statistically significant interaction between n--2 task repetition and n--2 response repetition [$F$(1, 38) = 1.3, $p$ = .26]; that is, there was no significant difference between n--2 task repetition costs for n--2 response repetitions and n--2 response switches. Mayr suggested this provided evidence against the episodic retrieval account of n--2 task repetition costs, and instead favours the inhibitory account.

\section{The Current Study}
The purpose of the current study was to re-examine the evidence for the effect of episodic retrieval on n--2 task repetition costs. The conclusion of \cite{Mayr2002} rests on the acceptance of a null hypothesis (i.e., no difference of n--2 task repetition costs), which cannot be achieved via standard null hypothesis significance testing \citep{Gallistel2009, Wagenmakers2007}; however, evidence in favour of a null hypothesis (given some data) can be obtained using Bayes factors \citep[e.g.,][]{Rouder2009}. The Bayes factor (denoted $BF_{10}$) quantifies the relative evidence provided by the data in favour of an alternative hypothesis (i.e., n--2 task repetition costs are different for response repetitions and response switches) over a null hypothesis (i.e., n--2 repetition costs are equivalent).

The Bayes factor for the critical statistical test from Mayr's (2002) study ($BF_{10}$ = 0.315)\footnote{For all Bayes factors reported in this paper we use a non-informative prior on the alternative hypothesis, which is assumed to be distributed as a Cauchy with scaling factor $r$ = 0.707.} suggests that the null hypothesis is about 3 times more likely than the alternative, given the data, which provides anecdotal-to-moderate support for the null \citep[e.g.,][]{Schoenbrodtinpress}. As this Bayesian analysis does not provide compelling evidence for the null, and given the importance of assessing to what extent (if any) episodic retrieval can influence n--2 task repetition costs in task switching, we were interested in performing a replication of Mayr's study to gather more evidence.

The current study replicated critical aspects of Mayr's (2002) design relevant to n--2 task repetitions. As Mayr's study was also interested in exploring to what extent the rule-switching paradigm generated typical task switching effects (such as switch costs, effects of preparation, and effects of the delay between tasks), we made some changes to the original design so that it was more tailored toward assessing n--2 task repetition costs. Specifically, immediate task repetitions were not allowed; it has been shown that including immediate task repetitions reduces the n--2 task repetition cost \citep{Philipp2006}, so we removed this possibility. We also did not manipulate preparation via the cue--stimulus interval, as Mayr reported no effect of this variable on n--2 task repetition costs. Mayr did find that n--2 repetition costs were larger with shorter response--cue intervals (RCI; the time between the response to one trial and the onset of the cue for the next trial), a typical finding for n--2 task repetition costs \citep{Gade2005, Grange2009, Mayr2000}. Therefore, in order to obtain larger n--2 task repetition costs we only used a short RCI.

%----------------------
\section{Method}

\subsection{Participants}
All participants were undergraduates at the School of Psychology at Keele University. Participants took part in exchange for partial course credit or a small cash payment (£6). Our final sample comprised 76 participants. Three additional participants were removed before analysis due to failure to maintain accuracy levels above 90\%.

Our sample size was determined via optional stopping. We used Sequential Bayes Factors \citep{Schoenbrodtinpress} to determine our stopping rule for participant recruitment. We were interested in establishing the presence or absence of an interaction between task sequence (ABA vs. CBA) and response repetition (repetition vs. switch). For the purposes of our stopping rule, this can be expressed as a default within-subjects Bayesian \emph{t}-test \citep{Rouder2009} comparing n--2 repetition costs for response repetitions and response switches.  We conducted a Bayesian \emph{t}-test on the data collected until the criterion for our a priori stopping rule was met. Specifically, our stopping rule required at least 20 participants; we continued data collection until $BF_{10}$ > 6 (constituting support for the alternative hypothesis) or $BF_{10}$ < 1/6 (constituting support for the null). \cite{Schoenbrodtinpress} demonstrated that a stopping rule of $BF_{10}$ > 6 (or $BF_{10}$ < 1/6) provided the best balance between type 1 and type 2 error, and was their recommended value for studies utilising Sequential Bayes Factors.

\subsection{Apparatus \& Stimuli}
Stimuli were presented on a 17in. monitor connected to a PC running E-Prime v. 2.0 software. The stimulus display consisted of an 8cm by 8cm square frame. A black circle (diameter = 1 cm.) served as the trial stimulus. Possible cues were the words ``horizontal'', ``vertical'', or ``diagonal'', and were presented in size 22 black Verdanna font directly above the stimulus frame. Responses were collected via a 1-ms. precise USB keyboard.

\subsection{Procedure}
On each trial a cue was presented above the frame for 150ms. After this time, the circle stimulus appeared in one of the four corners of the frame. The cue remained on the screen during stimulus presentation. The task required participants to mentally make a spatial transformation of the stimulus' location according to the rule dictated by the task cue, and to make a spatially-congruent response to this translated location. For example, if the stimulus was in the top-right corner of the frame, the participant would need to make a top-left response if the task was ``horizontal'', a bottom-right response if the task was ``vertical'', and a bottom-left response if the task was ``diagonal''. Responses were made on the numerical part of the keyboard, using the ``4'', ``5'', ``1'', and ``2'' keys for top-left, top-right, bottom-left, and bottom-right responses respectively. Participants were asked to respond as quickly and as accurately as possible, using the index finger of their right hand. In between trials, participants were asked to place their finger in the centre of the four response keys. Once a response was registered, the frame was cleared for a response--cue interval of 150ms, after which time a new cue appeared for the next trial. The cue for the next trial was chosen randomly with the constraint that task repetitions could not occur (cf., Mayr, 2002); the stimulus location was chosen randomly with no constraints on each trial. If participants made an error, the word ``Error!'' appeared in red for 1000ms above the stimulus frame (in the cue's position).

Participants were presented with 16 trials as practice. The practice block was repeated once if the participant made more than four errors. The main experiment presented 4 blocks of 120 trials.

\subsection{Design}
The experiment manipulated two factors in a fully-related design: \emph{Task Sequence} (n--2 task repetition [ABA] vs. n--2 task switch [CBA]) and \emph{Response Repetition} (n--2 response repetition vs. n-- response switch). The dependent variables were response time (RT) in milliseconds (ms.) and percent accuracy (\%).

%----------------------
\section{Results}
For response time analysis, the first two trials from each block were removed, as were error trials and the two trials following an error. Response times were trimmed by removing all RTs faster than 150ms, as well as any RTs slower than 2.5 standard deviations above the mean for each participant for each cell of the experimental design. Mean RTs and error rates can be seen in Table \ref{tab:behaviouralData}.

\begin{table*}[htbp]
\centering
\caption{Response times (RT) in milliseconds (ms) and accuracy (in percent) for ABA and CBA task sequences for response repetitions and response switches.}
\label{my-label}
\begin{tabular}{lccccc}
\hline
                    & \multicolumn{5}{c}{Task Sequence}                       \\ \cline{2-6} 
                    & \multicolumn{2}{c}{ABA}   &  & \multicolumn{2}{c}{CBA}  \\ \cline{2-3} \cline{5-6} 
                    & RT (ms)   & Accuracy (\%) &  & RT (ms)  & Accuracy (\%) \\ \hline
Response Repetition & 1000 (28) & 96.20 (0.39)  &  & 952 (28) & 96.36 (0.39) \\
Response Switch     & 1050 (29) & 95.02 (0.35)  &  & 964 (28) & 95.81 (0.34) \\ \hline
\end{tabular}
\label{tab:behaviouralData}
\end{table*}

\subsection{Response Times}
Response times were analysed via a two factor repeated measures analysis of variance (ANOVA) with the factors as described in \emph{Design}. There was a significant main effect of \emph{Sequence}, with slower RTs to ABA sequences (1,025ms) than to CBA sequences (958ms), $F$(1, 75) = 94.14, $p$<.001, $\eta_G^2$ = .018. The Bayes factor for this main effect was $BF_{10}$ = 1e+12, which provides substantial support for the presence of n--2 repetition costs. There was also a significant main effect of \emph{Response Sequence}, with faster RTs to response repetitions (976ms) than to response switches (1,007ms), $F$(1, 75) = 18.21, $p$<.001, $\eta_G^2$ = .004. The Bayes factor for this main effect was $BF_{10}$ = 338.77, which again provides substantial support for the alternative hypothesis. Critically, there was a significant interaction of both factors, $F$(1, 75) = 9.60, $p$<.01, $\eta_G^2$ = .001. The n--2 repetition cost was 48ms for response repetitions [$t$(75) = 4.2, $p$<.001; $BF_{10}$ = 271.24] and 86ms for response switches [$t$(75) = 13.0, $p$<.001; $BF_{10}$ = 7.11e+17].

The progression of the Sequential Bayes Factor for the interaction is shown in Figure \ref{fig:bayesFactor}. We stopped data collection after 76 participants, as at this point the criteria for our stopping rule had been reached\footnote{We could have stopped after 75 participants, but the last two participants were tested in successive sessions, so the Bayes factor was not checked until after the final participant.}. The final Bayes Factor for the difference of n--2 repetition costs for response repetitions and response switches was $BF_{10}$ = 9.97, which suggests that the alternative hypothesis is about 10 times more likely given than the data, which provides strong support that n--2 repetition costs are influenced by response repetitions.

\begin{figure*}
\begin{center}
\includegraphics[width = \textwidth]{Images/bayesFactor.pdf}
\caption{Progression of the Sequential Bayes Factor [expressed as log($BF_{10}$)] as sample size increased. The criteria for a priori stopping rules are shown as dotted horizontal lines.}
\label{fig:bayesFactor}
\end{center}
\end{figure*}

\subsubsection{Robustness Check on Bayesian Priors}
We used a default prior distribution on the effect size for the alternative hypothesis in the Bayes factor analysis, which was assumed to be distributed as a Cauchy distribution with scale parameter $r$ = 0.707. To examine how robust our findings were to the choice of prior, we conducted a robustness check by re-calculating the Bayes factor across a wide range of priors by varying scale parameter $r$: As $r$ increases, the prior distribution becomes wider, reflecting a prior for larger effects; $r$s closer to zero make the distribution narrower, reflecting a prior for smaller effects. The robustness check is plotted in Figure \ref{fig:robustPrior}. This figure shows our conclusions (and our stopping rule) are robust to the prior used: Evidence favours the alternative hypothesis across all prior widths.

\begin{figure*}
\begin{center}
\includegraphics[width = \textwidth]{Images/robustPrior.pdf}
\caption{Robustness check of Bayes factor across a wide range of priors.}
\label{fig:robustPrior}
\end{center}
\end{figure*}

\subsubsection{Robustness of Recruitment Order on the Sequential Bayes Factor}
The progression of the Bayes Factor as sample size increased (Figure \ref{fig:bayesFactor}) appeared to provide slight evidence in favour of the null between sample sizes of 30 and 40, although the criterion for stopping was not reached. One might wonder, therefore, whether had a few more participants been recruited to the experiment showing a null interaction would we have stopped data collection and found evidence in favour of the null? Put another way, did recruitment order bias our results?

>>>>

\note{{\bf Word Count:} 7,125 (Main body \& references, not including abstract.)}
% 577 words in references.
% \note{{\bf Under Review---Please, no direct quotes.}}

@@

\authornote{Please address correspondence to James A. Grange, School of Psychology, Dorothy Hodgkin Building, Keele University, Keele, UK, ST5 5BG. Email: grange.jim@gmail.com. All raw data and analysis code are available to download at http://bit.ly/1P5cd0G.}

@@

\abstract{Inhibition in task switching is inferred from n--2 repetition costs: the observation that AB$A$ task switching sequences are responded to slower than CB$A$ sequences. This is thought to reflect the persisting inhibition of task A, which slows re-activation attempts. \cite{Mayr2002} reported an experiment testing a critical non-inhibitory account of this effect, namely episodic retrieval: If the trial parameters for task A match across an ABA sequence, responses should be facilitated due to priming from episodic retrieval; a cost would occur if trial parameters mismatch. In a rule-switching paradigm, Mayr reported no significant difference in n--2 repetition cost when the trial parameters repeated or switched across an ABA sequence, in clear contrast to the episodic retrieval account. What remains unclear is whether successful episodic retrieval \emph{modulates} the n--2 repetition cost. Across three experiments---including a close replication of Mayr (2002)---we find clear evidence of reduced n--2 task repetition costs when episodic retrieval is controlled. We find that the effect of episodic retrieval on the n--2 task repetition cost is increased when the cue--task relationship is made more abstract, suggesting the effect is due to interference in establishing the relevant attentional set. We also demonstrate that the episodic retrieval effect is not influenced by retrieval of low-level, perceptual, elements. Together, the data suggest the n--2 task repetition cost---typically attributable to an inhibitory mechanism---is largely explained by episodic retrieval effects.}

\keywords{Task switching; inhibition, n--2 repetition cost, episodic retrieval, cognitive control}

@@

How the cognitive system solves the stability--flexibility dilemma has been studied using the task switching paradigm \citep{Grange2014a,Kiesel2010,Vandierendonck2010}, wherein participants have to make speeded responses to simple cognitive tasks. For example, participants might be presented with number stimuli, and be asked to switch between judging whether the stimulus is odd/even or lower/higher than five. One cognitive process thought to be essential for task switching performance is the inhibition of competing tasks. Evidence for inhibition comes from the backward inhibition paradigm \citep{Koch2010, Mayr2000}, where participants are required to switch between three tasks (A, B, and C).  It is a consistent finding that AB$A$ task switching sequences are performed slower and with less accuracy than CB$A$ sequences. This effect---know as the \emph{n--2 task repetition cost}---is thought to reflect the persisting inhibition of task A in an ABA sequence, which hinders its re-activation in the last trial of the triplet.

The n--2 task repetition cost is important as it is believed to be a good measure of cognitive inhibition as the n--2 task repetition cost appears to be robust against non-inhibitory explanations \citep{Mayr2007}. One potential explanation of the n--2 task repetition cost that does not assume inhibition was explored by \cite{Mayr2002}. This \emph{episodic retrieval} account \citep{Neill1997} suggests (adapted to a task switching context) that when a task has been performed an episodic trace of trial parameters (such as the cue, stimulus characteristics, and the response made) is stored in memory. When this task is cued again, retrieval of the most recent episodic trace occurs. If the parameters of the presented trial differ from that of the retrieved episode (e.g., a different response is required), a mismatch cost occurs relative to if the retrieved episode matches parameters of the current trial (which will prime performance). Thus, according to this account, n--2 task repetition costs reflect a mismatch cost, as trial parameters typically differ between both instances of task A in an ABA sequence.

\cite{Mayr2002} assessed this alternative explanation by developing a paradigm where the match between trial parameters (i.e., the cue, the stimulus, and the response) across an ABA sequence could be manipulated (see Figure \ref{fig:mayrExperiment}). Participants were required to apply a spatial transformation of a target's location according to one of three stimulus--response rules (vertical, horizontal, or diagonal transformations). For example, if the target is in the bottom-left of the display and the current rule is ``vertical'', the correct response would be an upper-left response (as this reflects a vertical transformation of a bottom-left target). The parameters that might be stored in an episodic trace include (at least) the cue presented, the target's location, and the response made. This paradigm is able to test the episodic retrieval account of n--2 task repetition costs because trial parameters can either match or mismatch across n--2 task repetitions\footnote{Note that with one cue per task, the cue for task A will always be the same across an ABA sequence.}. For example, if the target is in the same location for task A across an ABA sequence, the same response will be required (i.e., an n--2 response repetition). In this case, the episodic retrieval account would predict facilitated performance (i.e., an n--2 task repetition \emph{benefit}). An n--2 response switch, however, would produce an n--2 task repetition cost as there is a mismatch between trial parameters and the retrieved episodic trace (i.e., the response required).

\begin{figure}
\begin{center}
\includegraphics[width = \textwidth]{Images/mayrExperiment.pdf}
\caption{Schematic overview of Mayr's (2002) experimental procedure. The arrows are not displayed to participants, but reflect the spatial transformation required according to the given rule. }
\label{fig:mayrExperiment}
\end{center}
\end{figure}

\cite{Mayr2002} found no statistically significant interaction between n--2 task repetition and n--2 response repetition [$F$(1, 38) = 1.3, $p$ = .26]; that is, there was no significant difference between n--2 task repetition costs for n--2 response repetitions and n--2 response switches. This provides clear evidence against the episodic retrieval account of n--2 task repetition costs, and instead supports the inhibitory account.

\section{The Current Study}
Although Mayr's (2002) study provides clear evidence against episodic retrieval being the \emph{sole} explanation of n--2 task repetition costs, it is not clear from this study whether episodic retrieval has any modulatory effect on this measure of inhibition. Indeed, as Mayr notes in his conclusion, despite the non-significance of the critical interaction, a numerical trend of smaller n--2 task repetition costs for n--2 response repetitions was present in the data. However, the lack of a significant interaction cannot be taken as evidence supporting no modulatory effect, as accepting a null hypothesis cannot be achieved via standard null hypothesis significance testing \citep{Gallistel2009, Wagenmakers2007}; however, evidence in favour of a null hypothesis (given some data) can be obtained using Bayes factors \citep[e.g.,][]{Rouder2009}. The Bayes factor (denoted $BF_{10}$) quantifies the relative evidence provided by the data in favour of an alternative hypothesis (i.e., n--2 task repetition costs are different for response repetitions and response switches) over a null hypothesis (i.e., n--2 task repetition costs are equivalent).

The Bayes factor for the critical statistical test from Mayr's (2002) study ($BF_{10}$ = 0.315)\footnote{For all Bayes factors reported in this paper we use a non-informative prior on the alternative hypothesis, which is assumed to be distributed as a Cauchy with scaling factor $r$ = 0.707.} suggests that the null hypothesis is about three times more likely than the alternative, given the data, which provides anecdotal-to-moderate support for the null \citep[e.g.,][]{Schoenbrodtinpress}. As this Bayesian analysis does not provide compelling evidence for the null, and given the importance of assessing to what extent (if any) episodic retrieval can influence n--2 task repetition costs in task switching, we were interested in investigating this question further.

The purpose of the current study was to re-examine the evidence for the effect of episodic retrieval on n--2 task repetition costs in a series of Experiments. In Experiment 1, we report a close replication of Mayr's (2002) design, and find that the n--2 task repetition cost is modulated by episodic retrieval. We follow this main finding up in two experiments. In Experiment 2, we manipulate the cue--task transparency---that is, ``\emph{...the degree to which the cue exogenously provides or directly stimulates the relevant [working memory] representations}'' \citep[][p.1004]{Grange2009}. Non-transparent cues require more processing in working memory to establish the relevant attentional set in comparison to transparent cues which require little or no processing in working memory to establish the relevant attentional set \citep[e.g.,][]{Grange2009, Grange2010, Grange2015a, Houghton2009, Mayr2000a}. If the episodic retrieval effect observed in Experiment 1 is caused by interference in working memory establishing a relevant attentional set, then we should observe larger episodic retrieval effects on the n--2 repetition cost under conditions of non-transparent cues; we find strong evidence for such an effect. In a final Experiment, we investigate whether the episodic retrieval effect is sensitive to low-level perceptual details---in particular, task-irrelevant aspects of the stimulus display---and find that it is not. Together, these results provide evidence that the n--2 repetition cost in task switching---typically described as a ``pure'' measure of cognitive inhibition---is heavily influenced by episodic retrieval effects.

%----------------------
\section{Experiment 1}

In Experiment 1, we wished to replicate critical aspects of Mayr's (2002) design relevant to n--2 task repetitions. As Mayr's study was also interested in exploring to what extent the rule-switching paradigm generated typical task switching effects (such as switch costs, effects of preparation, and effects of the delay between tasks), we made some changes to the original design so that it was more tailored toward assessing n--2 task repetition costs. Specifically, immediate task repetitions were not allowed; it has been shown that including immediate task repetitions reduces the n--2 task repetition cost \citep{Philipp2006}, so we removed this possibility. We also did not manipulate preparation via the cue--stimulus interval, as Mayr reported no effect of this variable on n--2 task repetition costs. Mayr did find that n--2 repetition costs were larger with shorter response--cue intervals (RCI; the time between the response to one trial and the onset of the cue for the next trial), a typical finding for n--2 task repetition costs \citep{Gade2005, Grange2009, Mayr2000}. Therefore, in order to obtain larger n--2 task repetition costs we only used a short RCI.

\subsection{Method}

\subsubsection{Participants}
All participants were undergraduates at the School of Psychology at Keele University. Participants took part in exchange for partial course credit or a small cash payment (£6). Our final sample comprised 76 participants. The stopping rule utilised a Bayesian sequential analysis, which is detailed in Appendix A. Three additional participants were removed before analysis due to failure to maintain accuracy levels above 90\%.

\subsubsection{Apparatus \& Stimuli}
Stimuli were presented on a 17in. monitor connected to a PC running E-Prime v. 2.0 software. The stimulus display consisted of an 8cm by 8cm square frame. A black circle (diameter = 1 cm.) served as the trial stimulus. Possible cues were the words ``horizontal'', ``vertical'', or ``diagonal'', and were presented in size 22 black Verdanna font directly above the stimulus frame. Responses were collected via a 1-ms. precise USB keyboard.

\subsubsection{Procedure}
On each trial a cue was presented above the frame for 150ms. After this time, the circle stimulus appeared in one of the four corners of the frame. The cue remained on the screen during stimulus presentation. The task required participants to mentally make a spatial transformation of the stimulus' location according to the rule dictated by the task cue, and to make a spatially-congruent response to this translated location. For example, if the stimulus was in the top-right corner of the frame, the participant would need to make a top-left response if the task was ``horizontal'', a bottom-right response if the task was ``vertical'', and a bottom-left response if the task was ``diagonal''. Responses were made on the numerical part of the keyboard, using the ``4'', ``5'', ``1'', and ``2'' keys for top-left, top-right, bottom-left, and bottom-right responses respectively. Participants were asked to respond as quickly and as accurately as possible, using the index finger of their right hand. In between trials, participants were asked to place their finger in the centre of the four response keys. Once a response was registered, the frame was cleared for a response--cue interval of 150ms, after which time a new cue appeared for the next trial. The cue for the next trial was chosen randomly with the constraint that task repetitions could not occur (cf., Mayr, 2002); the stimulus location was chosen randomly with no constraints on each trial. If participants made an error, the word ``Error!'' appeared in red (same size \& font as cues) for 1000ms above the stimulus frame (in the cue's position).

Participants were presented with 16 trials as practice. The practice block was repeated once if the participant made more than four errors. The main experiment presented four blocks of 120 trials.

\subsubsection{Design}
The experiment manipulated two factors in a fully-related design: \emph{Task Sequence} (n--2 task repetition [ABA] vs. n--2 task switch [CBA]) and \emph{Response Repetition} (n--2 response repetition vs. n--2 response switch). The dependent variables were response time (RT) in milliseconds (ms.) and percent accuracy (\%).

\subsection{Results}
For response time analysis, the first two trials from each block were removed, as were error trials and the two trials following an error. These trials cannot be classified as ABA or CBA sequences. Response times were trimmed by removing all RTs faster than 150ms, as well as any RTs slower than 2.5 standard deviations above the mean for each participant for each cell of the experimental design. Mean RTs and error rates can be seen in Table \ref{tab:Experiment1}.

We present our results using standard null hypothesis significance testing (NHST), as well as Bayesian analysis (Bayes factors). All analysis was conducted using \texttt{R} statistics \citep{RCore2015}. Bayesian analysis utilised the \texttt{BayesFactor} package \citep{Morey2015} and the \texttt{BEST} package \citep{Kruschke2013}.

\begin{table*}[htbp]
\centering
\caption{Response times (RT) in milliseconds (ms) and accuracy (in percent) for ABA and CBA task sequences for response repetitions and response switches in Experiment 1.}
\begin{tabular}{lccccc}
\hline
                    & \multicolumn{5}{c}{Task Sequence}                       \\ \cline{2-6} 
                    & \multicolumn{2}{c}{ABA}   &  & \multicolumn{2}{c}{CBA}  \\ \cline{2-3} \cline{5-6} 
                    & RT (ms)   & Accuracy (\%) &  & RT (ms)  & Accuracy (\%) \\ \hline
N--2 Response Repetition & 1000 (28) & 96.20 (0.39)  &  & 952 (28) & 96.36 (0.39) \\
N--2 Response Switch     & 1050 (29) & 95.02 (0.35)  &  & 964 (28) & 95.81 (0.34) \\ \hline
\end{tabular}
\label{tab:Experiment1}
\end{table*}

\subsubsection{Response Times} 
Response times were analysed via a two factor repeated measures analysis of variance (ANOVA) with the factors \emph{Task Sequence} and \emph{Response Repetition}. There was a significant main effect of Task Sequence, with slower RTs to ABA sequences (1,025ms) than to CBA sequences (958ms), $F$(1, 75) = 94.14, $p$<.001, $\eta_G^2$ = .018. The Bayes factor for this main effect was $BF_{10}$ = 1e+12, which provides substantial support for the presence of n--2 task repetition costs. There was also a significant main effect of Response Repetition, with faster RTs to n--2 response repetitions (976ms) than to n--2 response switches (1,007ms), $F$(1, 75) = 18.21, $p$<.001, $\eta_G^2$ = .004. The Bayes factor for this main effect was $BF_{10}$ = 338.77, which again provides substantial support for the alternative hypothesis. Critically, there was a significant interaction of both factors, $F$(1, 75) = 9.60, $p$<.01, $\eta_G^2$ = .001. The n--2 task repetition cost was 48ms for n--2 response repetitions [$t$(75) = 4.2, $p$<.001; $BF_{10}$ = 271.24] and 86ms for n--2 response switches [$t$(75) = 13.0, $p$<.001; $BF_{10}$ = 7.11e+17].

\paragraph{Bayesian Analysis}

The final Bayes Factor for the difference of n--2 task repetition costs for n--2 response repetitions and response switches was $BF_{10}$ = 9.97, which suggests that the alternative hypothesis is about 10 times more likely given the data, which provides strong support that n--2 task repetition costs are influenced by n--2 response repetitions. Due to the theoretical importance of this finding, we provide more detailed Bayesian analysis and robustness checks in Appendix B.

\subsubsection{Accuracy}
Accuracy analysis showed no significant effect of Task Sequence [$F$(1, 75) = 3.36, $p$=.07, $\eta_G^2$ = .006]; the Bayes factor for this main effect was $BF_{10}$ = 0.618, which provides only anecdotal support for the null. The main effect of Response Repetition was significant [$F$(1, 75) = 12.17, $p$<.001, $\eta_G^2$ = .019], suggestive of better accuracy for n--2 response repetitions (96.28\%) than for response switches (95.41\%). The Bayes factor was $BF_{10}$ = 29.66, which provides strong support for the alternative. The interaction was not significant [$F$(1, 75) = 1.32, $p$=.25, $\eta_G^2$ = .003]; the Bayes factor was $BF_{10}$ = 0.238, which provides moderate support for the null hypothesis.

%----------------------
\subsection{Discussion}
Experiment 1 sought to re-examine the evidence for a modulatory effect of episodic retrieval on n--2 task repetition costs in task switching by replicating key aspects of Mayr's (2002) study. In contrast to that study, we found clear evidence of episodic retrieval influencing n--2 task repetition costs in task switching; specifically, n--2 task repetition costs were smaller when the response repeated over an ABA sequence compared to when the response switched. This is in line with episodic retrieval facilitating responding when trial parameters match over an ABA sequence (i.e., for n--2 response repetitions). This finding questions the common interpretation of the n--2 task repetition cost as a ``pure'' measure of task inhibition \citep{Koch2010, Mayr2007}.

%----------------------
\section{Experiment 2}
We wished to follow the findings from Experiment 1 by testing some of the boundary conditions of the effect. In particular, we were interested in whether manipulating the cue--task transparency modulated the observed episodic retrieval effect on the n--2 repetition cost. Recall that non-transparent cues require more processing in working memory to establish the relevant attentional set in comparison to transparent cues which require little or no processing in working memory to establish the relevant attentional set \citep[e.g.,][]{Grange2009, Grange2010, Grange2015a, Houghton2009, Mayr2000a}. In the case of Experiment 1, the word cues are relatively transparent in that the words clearly cue the relevant rule. An example of a non-transparent cue would be arbitrary shapes paired with each task (e.g., a square cue for the ``diagonal'' task).

Investigating the effect of cue--task transparency was of interest as there is good evidence that non-transparent cues increase the magnitude of the n--2 task repetition cost relative to transparent cues \citep[e.g.,][]{Gade2014, Grange2009, Grange2010, Houghton2009}. Such increases in the n--2 task repetition cost have been interpreted as reflecting an increased need for inhibition. For example \cite{Houghton2009} suggested that non-transparent cues require a process of ``translation'' between the cue and the elements of the task-set required; based on \cite{Mayr2000a}, they suggested this translation involves retrieval of task-set elements from long-term memory and their application in working memory. During a task switch, newly-retrieved elements will conflict with the still-active elements in working memory from the previous task; this interference is resolved by inhibition. Houghton et al. hypothesised that transparent cues do not lead to such interference as the cue provides the desired contents of working memory directly, and as such interference from elements active on the previous trial is minimal. In several studies, Houghton and colleagues \citep{Grange2009, Grange2010, Houghton2009} found evidence that the n--2 task repetition cost is larger for non-transparent cues, and often absent for highly-transparent cues \citep[but see][for a discussion on interpreting null n--2 task repetition costs]{Grange2013}.

However, given the findings of our Experiment 1, this pattern of data could also be explained under a model of episodic retrieval being influenced by cue transparency, rather than inhibition per se. For example, if the larger n--2 task repetition cost under conditions of episodic mismatch from Experiment 1 was occurring due to conflict between the task-set elements retrieved from episodic memory (from n--2) and the current task parameters in working memory, then reducing the need for working memory in establishing the currently-relevant task-set should reduce this interference. That is, with highly-transparent cues, the need for working memory processing to establish the relevant attentional set is reduced as the cue provides the necessary elements to perform the task successfully; therefore, the parameters retrieved from episodic memory will not interfere with anything.

Under this hypothesis, the effect of episodic retrieval on the n--2 task repetition cost should be greater under conditions of non-transparent cues. If such a pattern is found, it questions the conclusion that reduced cue-transparency increases the need for inhibition; instead, it would suggest that cue-transparency is influencing episodic interference in working memory.

To test this, we performed a conceptual replication of Experiment 1, but changed the nature of the task cue in two (within-subject) conditions (see Figure \ref{fig:cues_Experiment2}): In the ``shape'' cue condition, the cues were non-transparent, having no pre-experimental association with the task rules, for example a square cue indicating the ``diagonal'' judgment. In contrast, the ``arrow'' cues condition, the cue provides a direct sample of the response rules relevant for the current trial. For example, the ``vertical'' judgment is cued by two up--down arrows. We predicted that the effect of episodic retrieval on the n--2 task repetition cost would be greater for the Shape cues compared to the Arrow cues.

\subsection{Method}
\subsubsection{Participants}
The stopping rule for Experiment 2 is detailed in Appendix A. All participants were from the same pool as Experiment 1, receiving the same compensation. None had taken part in Experiment 1. Our final sample consisted of 66 participants.
